Multi-channel Kondo model URG

### 2021-11-03 multi-channel-urg.tex
completed second order Kondo URG, everything matches perfectly

\begin{equation}\begin{aligned}
	H = \sum_{k,\sigma,\gamma}\epsilon_{k}^\gamma \hat n^\gamma_{k\sigma} + J\sum_{kk^\prime,\gamma} \vec{S_d}\cdot\vec{s}_{\alpha\alpha^\prime}{c^\gamma_{k\alpha}}^\dagger c^\gamma_{k^\prime\alpha^\prime}
\end{aligned}\end{equation}
\begin{equation}\begin{aligned}
	\Delta H = \tau\left(c^\dagger T \frac{1}{\hat \omega - H_D}T^\dagger c + T^\dagger c \frac{1}{\hat \omega - H_D}c^\dagger T\right)
\end{aligned}\end{equation}

@@

	\text{term 3} = \frac{J^2\left(\omega^\prime - \frac{1}{2}D\right)|\delta D|}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}\sum_{k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^a  S_d^b \left(s^a s^b\right)_{\alpha^\prime \alpha} = \text{term 1}

@@

>>>>

\begin{equation}\begin{aligned}
	H = \sum_{k,\sigma,\gamma}\epsilon_{k}^\gamma \hat n^\gamma_{k\sigma} + J\sum_{kk^\prime,\gamma} \vec{S_d}\cdot\vec{s}_{\alpha\alpha^\prime}{c^\gamma_{k\alpha}}^\dagger c^\gamma_{k^\prime\alpha^\prime}
\end{aligned}\end{equation}
\begin{equation}\begin{aligned}
	\Delta H = \left[c^\dagger T, \eta \right] = \left(c^\dagger T \frac{1}{\hat \omega - H_D}T^\dagger c - T^\dagger c \frac{1}{\hat \omega - H_D}c^\dagger T\right)
\end{aligned}\end{equation}

@@

	\text{term 3} = \frac{J^2\left(\omega^\prime - \frac{1}{2}D\right)|\delta D|}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}\sum_{k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^a  S_d^b \left(s^a s^b\right)_{\alpha^\prime \alpha} = \frac{1}{2}\frac{J^2\left(\omega^\prime - \frac{1}{2}D\right)|\delta D|}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \sum_{k k^\prime \alpha \alpha^\prime,c} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} \vec{S_d}\cdot\vec{s}_{\alpha^\prime \alpha}

@@

\subsection{Total renormalization}
From the formula for the renormalization \(\Delta H\), we write
\begin{equation}\begin{aligned}
	\Delta H = \frac{1}{2}\left(\text{term 3} + \text{term 4} - \text{term 1} - \text{term 2}\right)
\end{aligned}\end{equation}
From the constraints of URG and particle-hole symmetry, we have the constraint \(\omega + \omega^\prime = H_d^0 + H_d^1\). \(H_d^0\) is the diagonal part when the current node is unoccupied and \(H_d^1\) is when its occupied. For our case, \(H_d^0 + H_d^1 = \sum \epsilon_q \tau_q = D\), because both the hole and particle states have energy of \(\frac{D}{2}\) (\(\epsilon_q\) and \(\tau\) flip sign together). We therefore have \((\omega - D/2) = -(\omega^\prime - D/2)\). term 2 and term 4 cancel each other and term 3 becomes equal to term 1. The total renormalization at second order is therefore (relabelling \(\omega^\prime\) as \(\omega\))
\begin{equation}\begin{aligned}
	\Delta H = \text{term 3} = \frac{1}{2}\frac{J^2\left(\omega - \frac{1}{2}D\right)|\delta D|}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \sum_{k k^\prime \alpha \alpha^\prime,c} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} \vec{S_d}\cdot\vec{s}_{\alpha^\prime \alpha}
\end{aligned}\end{equation}
which gives
\begin{equation}\begin{aligned}
	\Delta J = \frac{1}{2}\frac{J^2\left(\omega - \frac{1}{2}D\right)|\delta D|}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}
\end{aligned}\end{equation}
The choice of \(\omega = D\) gives
\begin{equation}\begin{aligned}
	\Delta J = \frac{J^2 D |\delta D|}{D^2 - \frac{1}{4}J^2}
\end{aligned}\end{equation}
For \(J \ll D\), we get the one-loop PMS form.
